---
title: "AIC: Analysis"
format: html
editor_options: 
  chunk_output_type: console
---

## Setup
### Loading packages

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyLPA)
library(gt)
library(here)
library(psych)
```

### Load custom functions

```{r m}
source(here::here("R/utils.R"))
```

### Read data

```{r message=FALSE}
processed <- readr::read_csv(here::here("data/processed/aic_processed_data.csv"))
# colnames(processed)

processed <- processed |>
  mutate(
    is_ai = case_when(is_ai == 0L ~ "No",
                      is_ai == 1L ~ "Yes"),
    is_responsibility = case_when(is_responsibility == 0L ~ "No",
                                  is_responsibility == 1L ~ "Yes"),
    row_id = row_number()
  )
```

### Demographic analysis

```{r}
processed |>
  select(k02_01, k02_03, k02_04, k02_05) |>
  pivot_longer(cols = everything(), names_to = "variable") |>
  calculate_percentage(response_var = value, grouping_var = variable) |>
  mutate(
    variable = case_when(
      variable == "k02_01" ~ "Gender",
      variable == "k02_03" ~ "Mother's highest education",
      variable == "k02_04" ~ "Father's highest education",
      variable == "k02_05" ~ "Economic status"
    ),
    factor = if_else(!duplicated(variable), variable, NA_character_)
  ) |>
  select(factor, value, n, percentage) |>
  gt() |>
  tab_options(table.font.size = "small") |>
  fmt_missing(columns = everything(), missing_text = "") |>
  cols_label(
    value = md("**Value**"),
    n = md("**N**"),
    percentage = md("**Percentage**"),
    factor = md("**Factor**")
  )
  # gtsave(filename = here(paste0("tables/demographic", ".tex")))
```

How often do you use ChatGPT or other generative AI tools?

```{r}
processed |> 
  calculate_percentage(response_var = k03_01) |> 
  mutate(
    k03_01 = case_when(
      k03_01 == "Soha" ~ "Never",
      k03_01 == "Naponta" ~ "Daily",
      k03_01 == "Naponta többször" ~ "Multiple times daily",
      k03_01 == "Hetente egyszer" ~ "Once a week",
      k03_01 == "Hetente többször" ~ "Multiple times weekly",
      k03_01 == "Havonta kevesebb mint egyszer" ~ "Less than once monthly",
      k03_01 == "Havonta egyszer" ~ "Once monthly"
    ),
    k03_01 = factor(k03_01, levels = c("Never", "Daily", "Multiple times daily", "Once a week", "Multiple times weekly", "Less than once monthly", "Once monthly"))
  ) |> 
  arrange(k03_01) |> 
  select(-N, -relative_frequency) |> 
  rename(levels = k03_01) |> 
    gt() |>
  tab_options(table.font.size = "small") |>
  fmt_missing(columns = everything(), missing_text = "") |>
  cols_label(
    levels = md("**Levels**"),
    n = md("**N**"),
    percentage = md("**Percentage**"),
  ) 
  # gtsave(filename = here(paste0("tables/chatgpt_use", ".tex")))
```

Interaction between frequency of AI use and AI condition.

```{r}
processed |> 
  mutate(
    k03_01 = case_when(
      k03_01 == "Soha" ~ "Never",
      k03_01 == "Naponta" ~ "Daily",
      k03_01 == "Naponta többször" ~ "Multiple times daily",
      k03_01 == "Hetente egyszer" ~ "Once a week",
      k03_01 == "Hetente többször" ~ "Multiple times weekly",
      k03_01 == "Havonta kevesebb mint egyszer" ~ "Less than once monthly",
      k03_01 == "Havonta egyszer" ~ "Once monthly"
    ),
    k03_01 = factor(k03_01, levels = c("Never", "Daily", "Multiple times daily", "Once a week", "Multiple times weekly", "Less than once monthly", "Once monthly"))
  ) |> 
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = k03_01)
   # gtsave(filename = here(paste0("analysis/tables/chatgpt_use_ai_main", ".tex")))
```

```{r}
processed |> 
  mutate(
    k03_01 = case_when(
      k03_01 == "Soha" ~ "Never",
      k03_01 == "Naponta" ~ "Daily",
      k03_01 == "Naponta többször" ~ "Multiple times daily",
      k03_01 == "Hetente egyszer" ~ "Once a week",
      k03_01 == "Hetente többször" ~ "Multiple times weekly",
      k03_01 == "Havonta kevesebb mint egyszer" ~ "Less than once monthly",
      k03_01 == "Havonta egyszer" ~ "Once monthly"
    ),
    k03_01 = factor(k03_01, levels = c("Never", "Daily", "Multiple times daily", "Once a week", "Multiple times weekly", "Less than once monthly", "Once monthly"))
  ) |> 
  create_interaction_table(response_vars = c(k04_02_expertise, k04_02_integrity, k04_02_benevolence), grouping_var = is_ai, factor_var = k03_01) 
   # gtsave(filename = here(paste0("analysis/tables/chatgpt_use_ai_researchers", ".tex")))
```

### Main effects

AI use main effect.

```{r}
processed |>
  group_by(is_ai) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2)
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -is_ai,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = is_ai, values_from = values) |>
  pivot_wider(names_from = stat, values_from = c(No, Yes)) |>
  mutate(Difference = round(No_mean - Yes_mean, 2)) |> 
  mutate(
    No = paste(No_mean, No_sd, sep = "/"),
    Yes = paste(Yes_mean, Yes_sd, sep = "/")
  ) |>
  select(items, No, Yes, Difference) |> 
  outcome_var_rename(items) |> 
  gt() 
  # gtsave(filename = here(paste0("tables/ai_main", ".tex")))
```

Responsibility main effect.

```{r}
processed |>
  group_by(is_responsibility) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2),
      n = ~ n()
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -is_responsibility,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = is_responsibility, values_from = values) |>
  pivot_wider(names_from = stat, values_from = c(No, Yes)) |>
  mutate(mean_diff = round(No_mean - Yes_mean, 2),
         sd_diff = round(sqrt((No_sd ^ 2 / No_n) + (Yes_sd ^ 2 / Yes_n)), 2)) |>
  mutate(
    No = paste(No_mean, No_sd, sep = "/"),
    Yes = paste(Yes_mean, Yes_sd, sep = "/"),
    Difference = paste(mean_diff, sd_diff, sep = "/")
  ) |>
  select(items, No, Yes, Difference) |> 
  outcome_var_rename(items) |> 
  gt() 
  # gtsave(filename = here(paste0("tables/responsibility_main", ".tex")))
```

Tables for the main outcome variable based on demographic variables.

Gender.

```{r}
processed |>
  filter(k02_01 != "Wishes not to respond") |> 
  group_by(k02_01) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2)
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -k02_01,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = k02_01, values_from = values) |>
  pivot_wider(names_from = stat, values_from = c(Male, Female)) |>
  mutate(Difference = round(Male_mean - Female_mean, 2)) |>
  mutate(
    Male = paste(Male_mean, Male_sd, sep = "/"),
    Female = paste(Female_mean, Female_sd, sep = "/")
  ) |>
  select(items, Male, Female, Difference) |> 
  outcome_var_rename(items) |> 
  gt() 
  # gtsave(filename = here(paste0("tables/gender_main", ".tex")))
```

Mother's education.

```{r}
processed |>
  group_by(k02_03) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2)
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -k02_03,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = k02_03, values_from = values) |>
  pivot_wider(
    names_from = stat,
    values_from = c(
      `Elementary school`,
      Highschool,
      PhD,
      `University BA`,
      `University MA`
    )
  ) |>
  mutate(
    Difference = round(`Elementary school_mean` - PhD_mean, 2)
  ) |>
  mutate(
    `Elementary school` = paste(`Elementary school_mean`, `Elementary school_sd`, sep = "/"),
    Highschool = paste(Highschool_mean, Highschool_sd, sep = "/"),
    `University BA` = paste(`University BA_mean`, `University BA_sd`, sep = "/"),
    `University MA` = paste(`University MA_mean`, `University MA_sd`, sep = "/"),
    PhD = paste(PhD_mean, PhD_sd, sep = "/")
  ) |>
  select(
    items,
    `Elementary school`,
    Highschool,
    `University BA`,
    `University MA`,
    PhD,
    Difference
  ) |> 
  outcome_var_rename(items) |> 
  gt() 
  # gtsave(filename = here(paste0("tables/mother_main", ".tex")))
```

Father's education.

```{r}
processed |>
  group_by(k02_04) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2)
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -k02_04,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = k02_04, values_from = values) |>
  pivot_wider(
    names_from = stat,
    values_from = c(
      `Elementary school`,
      Highschool,
      PhD,
      `University BA`,
      `University MA`
    )
  ) |>
  mutate(
    Difference = round(`Elementary school_mean` - PhD_mean, 2)
  ) |>
  mutate(
    `Elementary school` = paste(`Elementary school_mean`, `Elementary school_sd`, sep = "/"),
    Highschool = paste(Highschool_mean, Highschool_sd, sep = "/"),
    `University BA` = paste(`University BA_mean`, `University BA_sd`, sep = "/"),
    `University MA` = paste(`University MA_mean`, `University MA_sd`, sep = "/"),
    PhD = paste(PhD_mean, PhD_sd, sep = "/")
  ) |>
  select(
    items,
    `Elementary school`,
    Highschool,
    `University BA`,
    `University MA`,
    PhD,
    Difference
  ) |> 
  outcome_var_rename(items) |> 
  gt()  
  # gtsave(filename = here(paste0("tables/father_main", ".tex")))
```

Economic status.

```{r}
processed |>
  group_by(k02_05) |>
  summarise(across(
    starts_with("k01_02_i"),
    list(
      mean = ~ round(mean(.x, na.rm = TRUE), 2),
      sd = ~ round(sd(.x, na.rm = TRUE), 2)
    ),
    .names = "{.col}-{.fn}"
  )) |>
  pivot_longer(
    -k02_05,
    names_to = c("items", "stat"),
    names_sep = "-",
    values_to = "values"
  ) |>
  pivot_wider(names_from = k02_05, values_from = values) |>
  pivot_wider(
    names_from = stat,
    values_from = c(
      `Bottom 30%`,
     `Middle 40%`,
     `Top 30%`
    )
  ) |>
  mutate(
    Difference = round(`Bottom 30%_mean` - `Top 30%_mean`, 2)
  ) |>
  mutate(
    `Bottom 30%` = paste(`Bottom 30%_mean`, `Bottom 30%_sd`, sep = "/"),
    `Middle 40%` = paste(`Middle 40%_mean`, `Middle 40%_sd`, sep = "/"),
    `Top 30%` = paste(`Top 30%_mean`, `Top 30%_sd`, sep = "/")
  ) |>
  select(
    items,
    `Bottom 30%`,
    `Middle 40%`,
`Top 30%`,
    Difference
  ) |> 
  outcome_var_rename(items) |> 
  gt()  
  # gtsave(filename = here(paste0("tables/economic_main", ".tex")))
```

### Interaction

Interaction effects for the main outcome variable between modifying factors and AI use.

Gender.

```{r}
gender_ai_interaction <-
  processed |>
  filter(k02_01 != "Wishes not to respond") |> 
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = k02_01)

# save_latex_table(gender_ai_interaction, filename = "gender_ai_interaction")

gender_ai_interaction
```

Mother's education. Excluded elementary school because of the low number of responses.

```{r}
count(processed, k02_03)

mother_ai_interaction <-
  processed |>
  filter(k02_03 != "Elementary school") |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = k02_03, factor_levels = c("Highschool", "University BA", "University MA", "PhD"))

# save_latex_table(mother_ai_interaction, filename = "mother_ai_interaction")

mother_ai_interaction
```

Father's education.

```{r}
count(processed, k02_04)

father_ai_interaction <-
  processed |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = k02_04, factor_levels = c("Elementary school", "Highschool", "University BA", "University MA", "PhD"))

# save_latex_table(father_ai_interaction, filename = "father_ai_interaction")

father_ai_interaction
```

Joined education of parents.

```{r}
parents_ai_interaction <-
  processed |> 
    create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = parents_education_groups, factor_levels = c("25% Bottom", "50% Median", "25% Top"))

# save_latex_table(parents_ai_interaction, filename = "parents_ai_interaction")

parents_ai_interaction
```

Economic status.

```{r}
count(processed, k02_05)

economic_ai_interaction <- 
  processed |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = k02_05)

# save_latex_table(economic_ai_interaction, filename = "economic_ai_interaction")

economic_ai_interaction
```

Interaction effects for the main outcome variable between modifying factors and explicit responsibility.

Gender.

```{r}
gender_responsibility_interaction <-
  processed |>
  filter(k02_01 != "Wishes not to respond") |> 
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = k02_01)

# save_latex_table(gender_responsibility_interaction, filename = "gender_responsibility_interaction")

gender_responsibility_interaction
```

Mother's education. Excluded elementary school because of the low number of responses.

```{r}
mother_responsibility_interaction <-
  processed |>
  filter(k02_03 != "Elementary school") |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = k02_03, factor_levels = c( "Highschool", "University BA", "University MA", "PhD"))

# save_latex_table(mother_responsibility_interaction, filename = "mother_responsibility_interaction")

mother_responsibility_interaction
```

Father's education.

```{r}
father_responsibility_interaction <-
  processed |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = k02_04, factor_levels = c("Elementary school", "Highschool", "University BA", "University MA", "PhD"))

# save_latex_table(father_responsibility_interaction, filename = "father_responsibility_interaction")

father_responsibility_interaction
```

Joined education of parents.

```{r}
parent_responsibility_interaction <-
  processed |> 
    create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = parents_education_groups, factor_levels = c("25% Bottom", "50% Median", "25% Top"))

# save_latex_table(parent_responsibility_interaction, filename = "parent_responsibility_interaction")

parent_responsibility_interaction
```

Economic status.

```{r}
economic_responsibility_interaction <-
  processed |>
  create_interaction_table(response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = k02_05)

# save_latex_table(economic_responsibility_interaction, filename = "economic_responsibility_interaction")

economic_responsibility_interaction
```

### Latent Profile Analysis

 Run the analysis.
 
```{r}
# Filter the data for the LPA
renaming_map <- c(
   "ai_attitude_positive" = "k03_02_positive",
   "ai_attitude_negative" = "k03_02_negative",
   "science_attitude" = "k04_01_composite",
   "vehicle_ease_of_use" = "k06_01_ease_of_use",
   "vehicle_usefulness" = "k06_01_usefulness",
   "vehicle_safety_risk" = "k06_01_safety_risk",
   "vehicle_privacy_risk" = "k06_01_privacy_risk",
   "vehicle_trust" = "k06_01_trust",
   "vehicle_attitude" = "k06_01_attitude",
   "vehicle_intention_to_use" = "k06_01_intention_to_use"
)

lpa_data <- processed %>%
  dplyr::select(row_id, k03_02_positive, k03_02_negative, k04_01_composite, k06_01_ease_of_use, k06_01_usefulness, k06_01_safety_risk, k06_01_privacy_risk, k06_01_trust, k06_01_attitude, k06_01_intention_to_use) %>%
  dplyr::rename(!!!renaming_map)

lpa_data_scaled <- lpa_data %>%
  mutate(across(-row_id, ~ as.vector(scale(.))))

# Fit the model with 5 profiles
lpa_model <- estimate_profiles(dplyr::select(lpa_data_scaled, -row_id), n_profiles = 1:5, models = c(1, 2, 3, 6))

# View the summary of the model
lpa_model

# Get estimates
lpa_model6_class4 <- get_estimates(lpa_model$model_6_class_4)

lpa_model6_class4
```

Visualize the profiles

```{r}
plot_profiles(lpa_model)
```

```{r}
plot_profiles(lpa_model$model_6_class_4)
```

Get model fits

```{r}
get_fit(lpa_model) |>
  select(Model, Classes, BIC) |>
  mutate(is_min_bic = BIC == min(BIC, na.rm = T)) |>  # Identify the row with the lowest BIC
  gt() |>
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_column_labels()
  ) |>
  tab_style(
    style = list(cell_fill(color = "lightblue")),  # Highlight color for the row
    locations = cells_body(
      rows = is_min_bic
    )
  ) |>
  cols_hide(columns = is_min_bic) 

get_fit(lpa_model) |>
  select(Model, Classes, AIC) |>
  mutate(is_min_aic = AIC == min(AIC, na.rm = T)) |>  # Identify the row with the lowest BIC
  gt() |>
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_column_labels()
  ) |>
  tab_style(
    style = list(cell_fill(color = "lightblue")),  # Highlight color for the row
    locations = cells_body(
      rows = is_min_aic
    )
  ) |>
  cols_hide(columns = is_min_aic) 
```

Compare different profiles and modals

```{r}
compare_solutions(lpa_model, statistics = "BIC")
```

Sort participants to profiles.

```{r}
model_data <- get_data(lpa_model$model_6_class_4)

model_data <- model_data |> 
  mutate(row_id = lpa_data_scaled$row_id) 

processed_with_classes <- model_data %>%
  right_join(processed, by = "row_id") |> 
  mutate(
    Class = paste("class", Class, sep = "_")
  )
```

### Interaction effect by LPA classes

Exploring the interaction between LPA classes and AI use / responsibility on the main outcome variable.

```{r}
lpa_ai_abstract_interaction <-
create_interaction_table(processed_with_classes, response_vars = starts_with("k01_02_i"), grouping_var = is_ai, factor_var = Class)

# save_latex_table(lpa_ai_abstract_interaction, filename = "lpa_ai_abstract_interaction")

lpa_ai_abstract_interaction

lpa_responsibility_abstract_interaction <-
create_interaction_table(processed_with_classes, response_vars = starts_with("k01_02_i"), grouping_var = is_responsibility, factor_var = Class)

save_latex_table(lpa_responsibility_abstract_interaction, filename = "lpa_responsibility_abstract_interaction")

lpa_responsibility_abstract_interaction
```

Same but for the attitudes towards the researchers behind the presented abstract.

```{r}
lpa_ai_researcher_interaction <-
processed_with_classes |>
  create_interaction_table(response_vars = c(k04_02_expertise, k04_02_integrity, k04_02_benevolence), grouping_var = is_ai, factor_var = Class)

save_latex_table(lpa_ai_researcher_interaction, filename = "lpa_ai_researcher_interaction")

lpa_ai_researcher_interaction

lpa_responsibility_researcher_interaction <-
processed_with_classes |>
  create_interaction_table(response_vars = c(k04_02_expertise, k04_02_integrity, k04_02_benevolence), grouping_var = is_responsibility, factor_var = Class)

save_latex_table(lpa_responsibility_researcher_interaction, filename = "lpa_responsibility_researcher_interaction")

lpa_responsibility_researcher_interaction
```

### Testing the internal consistency of scales

Main outcome variable.

```{r}
main_outcome_scale <- processed %>%
  select(starts_with("k01_02_i"))

# Calculate Cronbach's alpha
psych::alpha(main_outcome_scale)
```

